---
title: "UNIT1_PPT"
author: "Maggie Sha"
date: "2020/10/19"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
library(png)
library(grid)
library(citation)
knitr::opts_chunk$set(echo = FALSE)
```

## Data

- USDA database selector
  * 13238 observations of 21 variables
  * NAs, empty columns, single repeated values
  * only 8 out of 21 columns containing meaningful data
  
## berry data

```{r import berry, echo = FALSE}
img=readPNG("berry.png")
grid.raster(img)
```

## Overview

- Data Cleaning and Organization
  * strawberry data
  * unfood data
  
- Visualization
  * Values of chemicals being used in 2016, 2018 and 2019 in all States
  * FUNGICIDE usage in California, Florida and Washington
  * PCA

## Data cleaning and Organization

- Filter out data other than strawberries
- Split the variables in one column into several different columns
- Eliminate Redundancy 
- Join columns to make the data meaningful
- Reorder columns
- filter chemicals being applied to food

## strawberry data

```{r import strawberries, echo = FALSE}
img=readPNG("straw.png")
grid.raster(img)
```

## chemicals being applied to food

```{r, echo=FALSE}
img=readPNG("unfood.png")
grid.raster(img)
```

## Values of chemicals being used in 2016, 2018 and 2019 in all States
```{r, echo = FALSE}
img=readPNG("line graph.png")
grid.raster(img)
```

## FUNGICIDE usage in California, Florida and Washington
```{r, echo = FALSE}
img=readPNG("bar.png")
grid.raster(img)
```

## PCA
```{r, echo = FALSE}
img=readPNG("pca.png")
grid.raster(img)
```

## References
```{r}
citation("knitr")
```
## References
```{r}

citation("citation")
```
## References
```{r}

citation("ggplot2")
```

## References
citation(package="tidyverse")

 Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source
  Software, 4(43), 1686, https://doi.org/10.21105/joss.01686